Programming Distributed Control Planes

### 2016-01-18 paper/regularir.tex

\section{Language}
\label{sec:language}

@@

     pol     &::=& p_1, \dots, p_n & \textit{constraints} \\
     p       &::=& p \leadsto r_1 \gg \dots \gg r_m & \textit{preferences} \\
     t       &::=& & \textit{test} \\
         &\BNFALT& true & \textit{true} \\
         &\BNFALT& \neg t & \textit{negation} \\
         &\BNFALT& t_1 \vee t_2 & \textit{disjunction} \\
         &\BNFALT& t_1 \wedge t_2 & \textit{conjunction} \\
         &\BNFALT& prefix = x & \textit{prefix test} \\
         &\BNFALT& comm = c & \textit{community test} \\
     r       &::=& & \textit{regular paths} \\ 
         &\BNFALT& n & \textit{AS number} \\
         &\BNFALT& in & \textit{internal loc} \\
         &\BNFALT& out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& !(r) & \textit{path negation} \\
         &\BNFALT& r^* & \textit{repetition} \\
     l       &::=& r_1 \rightarrow r_2 & \textit{link pairs} \\
     cc     &::=& agg(x, l) \BNFALT tag(c, t, l) & \textit{control constraints} \\
  \end{array} \]

>>>>

\section{Regular IR}
\label{sec:rir}

@@

     pol     &::=& p_1, \dots, p_n & \textit{constraints} \\
     p       &::=& t \text{ with } r_1 \gg \dots \gg r_m & \textit{preferences} \\
     t       &::=& & \textit{test} \\
         &\BNFALT& true & \textit{true} \\
         &\BNFALT& \neg t & \textit{negation} \\
         &\BNFALT& t_1 \vee t_2 & \textit{disjunction} \\
         &\BNFALT& t_1 \wedge t_2 & \textit{conjunction} \\
         &\BNFALT& prefix = x & \textit{prefix test} \\
         &\BNFALT& comm = c & \textit{community test} \\
     r       &::=& & \textit{regular paths} \\ 
         &\BNFALT& n & \textit{AS number} \\
         &\BNFALT& in & \textit{internal loc} \\
         &\BNFALT& out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& !(r) & \textit{path negation} \\
         &\BNFALT& r^* & \textit{repetition} \\
     l       &::=& r_1 \rightarrow r_2 & \textit{link pairs} \\
     cc     &::=& agg(x, l) \BNFALT tag(c, t, l) & \textit{control constraints} \\
  \end{array} \]
